---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# statascii

Create Stata-like tables in the R console

[![Travis build status](https://travis-ci.org/gvelasq/statascii.svg?branch=master)](https://travis-ci.org/gvelasq/statascii)
[![Coverage status](https://codecov.io/gh/gvelasq/statascii/branch/master/graph/badge.svg)](https://codecov.io/github/gvelasq/statascii?branch=master)
[![CRAN status](http://www.r-pkg.org/badges/version/statascii)](https://cran.r-project.org/package=statascii)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

## Installation

You can install statascii from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("gvelasq/statascii")
```

## Usage

```{r example, message = FALSE}
# setup
library(dplyr)
library(stringr)
library(statascii)

# a. demonstrate 'oneway' flavor for one-way tables of frequencies
a <- mtcars %>% count(gear) %>% rename(Freq. = n)
a <- a %>% add_row(gear = "Total", Freq. = sum(a[, 2]))
statascii(a, flavor = "oneway")

# b. demonstrate 'oneway' flavor with no padding
b <- mtcars %>% count(gear) %>% rename(Freq. = n)
b <- b %>% add_row(gear = "Total", Freq. = sum(b[, 2]))
statascii(b, flavor = "oneway", padding = "none")

# c. demonstrate 'twoway' flavor for n-way tables of frequencies
c <- mtcars %>% count(gear, carb, am) %>% rename(Freq. = n)
c <- c %>% ungroup() %>% add_row(gear = "Total", carb = "", am = "", Freq. = sum(c[, 4]))
statascii(c, flavor = "twoway")

# d. demonstrate 'twoway' flavor with dashed group separators
d <- mtcars %>% count(gear, carb, am) %>% rename(Freq. = n)
d <- d %>% ungroup() %>% add_row(gear = "Total", carb = "", am = "", Freq. = sum(d[, 4]))
statascii(d, flavor = "twoway", separators = TRUE)

# e. demonstrate 'summary' flavor for summary statistics
e <- mtcars %>% group_by(gear) %>% summarize(
  Obs = n(),
  Mean = mean(gear),
  "Std. Dev." = sd(gear),
  Min = min(gear),
  Max = max(gear)
)
statascii(e, flavor = "summary")

# f. demonstrate wrapping feature for wide tables
f <- mtcars %>%
  mutate(cyl2 = cyl, vs2 = vs, am2 = am, carb2 = carb) %>%
  filter(gear != 5) %>%
  count(gear, carb, am, vs, cyl, carb2, am2, vs2, cyl2) %>%
  rename(Freq. = n) %>%
  ungroup()
f <- f %>% add_row(gear = "Total", Freq. = sum(f[, 10]))
f[is.na(f)] <- ""
statascii(f, flavor = "oneway", separators = TRUE)
```

## Reference

`statascii()` borrows heavily from `asciify()`.

`asciify()` was written by @gavinsimpson in [StackOverflow](https://stackoverflow.com/questions/13011383) and [GitHub Gist](https://gist.github.com/gavinsimpson/2b49f3026b50eeba29314398e27a6770).

`statascii()` was written by @gvelasq in [Github Gist](https://gist.github.com/gvelasq/a39348f59f4353a9478704a28f86ed69) and now has its own [GitHub](https://github.com/gvelasq/statascii) package.

---
Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
